A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-08 paper.tex

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE:

@@

\section{Conclusions}
\label{section:conclusion}
By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.

>>>>

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:

@@

\section{Conclusions}
\label{section:conclusion}
By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.

In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.

Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service. The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers. Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
